Kimbee: A Speech Therapy Application For Children

### 2015-03-11 Paper/paper.tex
Spelling AND DONE BOYS

\subsection{Game ({\secit Kimbee})}
The {\em Game}, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech. It is written in TypeScript and compiled to optimized JavaScript. Since this system also performs speech processing to determine speech correctness, there are many interacting components. From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}. We target this project toward web technologies to allow wide distribution and adoption. From a design standpoint, we aimed to make each system loosely connected and non-disruptive to game-play. This required us to explore various new web technologies including HTML5 Web Workers for multi-threading and the UserMedia HTML5 API.

@@

\subsubsection{Speech Processing}
The {\em Speech Processing} of the {\em Game} handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multi-threaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in separate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\vspace{-3 pt}
\begin{enumerate}
  \item Web Workers are initialized to start processing the audio stream in parallel.
  \vspace{-6 pt}
  \item Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \vspace{-6 pt}
  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are queried for final results of their processing.
\end{enumerate}
\vspace{-3 pt}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.

>>>>

\subsection{Game ({\secit Kimbee})}
The {\em Game}, see Figure \ref{fig:tech}, is the system that the children interact with to practice speech. It is written in TypeScript and compiled to optimized JavaScript. Since this system also performs speech processing to determine speech correctness, there are many interacting components. From a high level, the major sub systems are: the {\em Phaser Game Implementation}, the {\em Speech Processing Component}, and the {\em Server Application Programming Interface (API)}. We target this project toward web technologies to allow wide distribution and adoption. From a design standpoint, we aimed to make each system loosely connected and non-disruptive to game-play. This required us to explore various new web technologies including HTML5 Web Workers for multiple threads and the UserMedia HTML5 API.

@@

\subsubsection{Speech Processing}
The {\em Speech Processing} of the {\em Game} handles all audio processing and speech related requests from the {\em Phaser Game Implementation}. Requests are made through an API Singleton that is constructed on game load. These include requests such as getting the next practice word for a particular speech problem, setting which speech problem the child is working on, and harvesting microphone data. Harvesting and processing microphone levels is a multi-threaded process implemented with HTML5 Web Workers. When the application is started and the API Singleton is constructed, audio stream {\em consumers} are created to process future audio streams in separate threads. Once a microphone ``Start'' request is made from the {\em Phaser Game Implementation}, the following steps are executed:
\vspace{-3 pt}
\begin{enumerate}
  \item Web Workers are initialized to start processing the audio stream in parallel.
  \vspace{-6 pt}
  \item Each stream buffer is processed by each Web Worker in parallel as the microphone streams raw Left-Right buffers.
  \vspace{-6 pt}
  \item Once a microphone ``Stop'' request is made from the {\em Phaser Game Implementation}, the consumers are then queried for final results of their processing.
\end{enumerate}
\vspace{-3 pt}
Currently there are two {\em consumers}: an {\em AudioStorageConsumer}, and a {\em RecognizerConsumer}. The {\em AudioStorageConsumer} simply stores the raw microphone levels, while the {\em RecognizerConsumer} communicates with the {\em CMU Sphinx} to iterate a best guess for the correctness of the child's speech.
